### 2019-11-14 cvpr_submission/introduction.tex
Minor corrections. Add or remove commas, Add \compresslist option for transfer learning section.

The impact of transfer learning is even more essential in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above (i.e. vision and language).
%One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
%In a typical VQA model, setting aside whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encoders and word embeddings is de facto standard, having empirically proven its dominance over the models trained from the ground up.
In this work, we focus on a parallel aspect of transfer learning in Image and Video QA. Both can be seen as meta-problems, where models have to develop different reasoning processes, associated to the type of questions (e.g., objects count queries, objects attribute queries etc.). We investigate, with a new model, whether mastering one task helps to master others. This is thus connected to multi-task learning~\cite{caruana1997multitask}.

>>>>

The impact of transfer learning is even more essential in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above (i.e., vision and language).
%One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
%In a typical VQA model, setting aside whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encoders and word embeddings is de facto standard, having empirically proven its dominance over the models trained from the ground up.
In this work, we focus on a parallel aspect of transfer learning in Image and Video QA. Both can be seen as meta-problems, where models have to develop different reasoning processes, associated to the type of questions (e.g., objects count queries, objects attribute queries etc.). We investigate, with a new model, whether mastering one task helps to master others. This is thus connected to multi-task learning~\cite{caruana1997multitask}.

### 2019-11-14 cvpr_submission/transfer_learning.tex
Minor corrections. Add or remove commas, Add \compresslist option for transfer learning section.

\begin{figure*}
	\centering
	\caption{Transfer learning taxonomy}
	\label{fig:taskonomy}
	\includegraphics[width=0.8\textwidth]{img/architecture/transfer_taxo}
\end{figure*}

We follow the notations in the survey by~\cite{pan2009survey}.
A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a marginal probability distribution.
For visual reasoning problems considered in this paper, 
$\cX$ will consist of purely visual inputs, i.e., either images or videos, in some cases, or 
a combination of both visual inputs and questions in other cases. 
A \emph{task} is a pair $\cT= (\cY,f(\cdot))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function. 
When the domain elements consist of both the question and the visual input, there is only one task, namely, to answer the 
question\footnote{%
	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas for typical video answering datasets,
	only a single answer is needed for the entire video.}. % 
If the domain elements consist of just the visual inputs, then the task is defined by the question so that each question 
defines a separate task.
\begin{definition}[\cite{pan2009survey}]
	\label{defn:transfer}
	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the 
	learning of the target predictive function $f_T(\cdot)$ in $\cD_T$ using the knowledge  in $\cD_S$ and $\cT_S$, where $\cD_S \ne \cD_T$, or $\cT_S \ne \cT_T$.
\end{definition}
In all our applications, $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the marginal distributions $P_S$ and $P_T$ are different.
Similarly, $\cT_S \ne \cT_T$ means that either $Y_S \ne Y_T$ or that the associated prediction functions are different.

Although~\cref{defn:transfer} is quite general, it does not adequately capture all the artifacts present in the visual reasoning.
For example, consider the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
but the marginal distributions $P_S$ and $P_T$ are different (referred to as \emph{domain adaptation}).
One setting is the case of static images, where this could be due to having different feature combinations in the source and
target but a different setting is in the context of video reasoning where the number of frames can be small in one case and 
large in another.
These require possibly very different methods, one involving building disentangled feature representations that can generalize across 
domains and another in which we might need memory-augmented neural networks that can generalize across frame lengths.
Another situation is when the questions themselves can be grouped into families such as count-based queries, 
comparison of objects, or existence of objects with certain features etc.
This entails studying transfer learning between families of tasks which requires extending the above definition.

Broadly, we consider 3 kinds of transfer learning problems in this work, as illustrated in~\cref{fig:taskonomy}. 
Let $\cQ$ denote the set of questions and $\cV$ denote the set of visual inputs.
\begin{description}
	\item[Feature Transfer:] In this setting of domain adaptation $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on $v$. The output set $\cY$ is the union of legitimate answers
	over all questions in $\cQ$.
	The marginal distributions $P_S$ and $P_T$ differ in just the feature attributes such as shape, color, and size, or their combinations
	thereof.

@@

	\item[Reasoning Transfer:]
	This setting requires an extension of~\cref{defn:transfer} given above to investigate transfer learning when
	grouping questions into families. Let $\cV$ be the feature space consisting of visual inputs only, shared by
	all tasks, with a common marginal distribution $P(X)$. For each question $q \in \cQ$, we define the task 
	$\cT_q = (\cY_q, f_q(\cdot))$ where
	the output set $\cY_q$ is the set of legitimate answers to $q$ and $f_q(v)$, for a visual input $v$, 
	is the answer to question $q$ on visual input $v$.
	Thus, tasks are in a 1-1 correspondence with questions.
	A \emph{task family} is a probability distribution on tasks which in our case can be obtained by defining the distribution on $\cQ$. 
	Given a task family, the goal is to learn a prediction function that gives an answer to $f_q(v)$ for $v \in \cV$ chosen according 
	to the feature space distribution and $q$ chosen according to the task probability distribution.
	Suppose $\cF_S$ is the source task family and $\cF_T$ is the target task family.
	Transfer learning aims to help improve the learning of the predictive function for the target task family 
	using the knowledge in the source task family.

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.8\textwidth]{img/architecture/transfer_taxo}
	\caption{Transfer learning taxonomy.}\label{fig:taskonomy}
\end{figure*}

We follow the notations in the survey by~\cite{pan2009survey}.
A \emph{domain} is a pair $\cD = (\cX,P(X))$, where $\cX$ is a feature space and $P(X)$ is a marginal probability distribution.
For visual reasoning problems considered in this paper, 
$\cX$ will consist of purely visual inputs, i.e., either images or videos in some cases, or 
a combination of both visual inputs and questions in other cases. 
A \emph{task} is a pair $\cT= (\cY,f(\cdot))$, where $\cY$ is a label space and $f: \cX \to \cY$ is a prediction function. 
When the domain elements consist of both the question and the visual input, there is only one task, namely, to answer the 
question\footnote{%
	For the COG dataset, the answer is a tuple, one for each frame in the video, whereas for typical video answering datasets,
	only a single answer is needed for the entire video.}. % 
If the domain elements consist of just the visual inputs, then the task is defined by the question so that each question 
defines a separate task.
\begin{definition}[\cite{pan2009survey}]
	\label{defn:transfer}
	Given a source domain $\cD_S$ and a source learning task $\cT_S$, a target domain $\cD_T$ and a target learning task $\cT_T$, transfer learning aims to help improve the 
	learning of the target predictive function $f_T(\cdot)$ in $\cD_T$ using the knowledge  in $\cD_S$ and $\cT_S$, where $\cD_S \ne \cD_T$, or $\cT_S \ne \cT_T$.
\end{definition}
In all our applications, $\cX_S = \cX_T$, so $\cD_S \ne \cD_T$ means that the marginal distributions $P_S$ and $P_T$ are different.
Similarly, $\cT_S \ne \cT_T$ means that either $Y_S \ne Y_T$ or that the associated prediction functions are different.

Although~\cref{defn:transfer} is quite general, it does not adequately capture all the artifacts present in visual reasoning.
For example, consider the transfer learning setting where the tasks $\cT_S$ and $\cT_T$ are the same 
but the marginal distributions $P_S$ and $P_T$ are different (referred to as \emph{domain adaptation}).
One setting is the case of static images, where this could be due to having different feature combinations in the source and
target but a different setting is in the context of video reasoning where the number of frames can be small in one case and 
large in another.
These require possibly very different methods, one involving building disentangled feature representations that can generalize across 
domains and another in which we might need memory-augmented neural networks that can generalize across frame lengths.
Another situation is when the questions themselves can be grouped into families such as count-based queries, 
comparison of objects, or existence of objects with certain features etc.
This entails studying transfer learning between families of tasks which requires extending the above definition.

Broadly, we consider 3 kinds of transfer learning problems in this work, as illustrated in~\cref{fig:taskonomy}. 
Let $\cQ$ denote the set of questions and $\cV$ denote the set of visual inputs.
\begin{description}
	\compresslist % used to reduce spacing
	\item[Feature Transfer:] In this setting of domain adaptation, $\cX_S = \cX_T \subseteq \cQ \times \cV$
	and the task $f(q,v)$ is just the answer to the question $q$ on $v$. The output set $\cY$ is the union of legitimate answers
	over all questions in $\cQ$.
	The marginal distributions $P_S$ and $P_T$ differ in just the feature attributes such as shape, color, and size, or their combinations
	thereof.

@@

	\item[Reasoning Transfer:]
	This setting requires an extension of~\cref{defn:transfer} above to investigate transfer learning when
	grouping questions into families. Let $\cV$ be the feature space consisting of visual inputs only, shared by
	all tasks, with a common marginal distribution $P(X)$. For each question $q \in \cQ$, we define the task 
	$\cT_q = (\cY_q, f_q(\cdot))$ where
	the output set $\cY_q$ is the set of legitimate answers to $q$ and $f_q(v)$, for a visual input $v$, 
	is the answer to question $q$ on visual input $v$.
	Thus, tasks are in a 1-1 correspondence with questions.
	A \emph{task family} is a probability distribution on tasks which in our case can be obtained by defining the distribution on $\cQ$. 
	Given a task family, the goal is to learn a prediction function that gives an answer to $f_q(v)$ for $v \in \cV$ chosen according 
	to the feature space distribution and $q$ chosen according to the task probability distribution.
	Suppose $\cF_S$ is the source task family and $\cF_T$ is the target task family.
	Transfer learning aims to help improve the learning of the predictive function for the target task family 
	using the knowledge in the source task family.
